\mytitle{}

### 2018-11-08 paper/paper.tex
Ability to selectively include results in table.

These flaws, poor handling of TCP traffic and high host density at egress points, catalyse and direct an exploration of the design space of RL models.
We improve the state-of-the-art through two agent classes designed to act on a per-flow basis, supported by an in-depth investigation of feature suitability and empirical evaluation.

>>>>

These flaws---poor handling of TCP traffic and high host density at egress points---catalyse and direct an exploration of the design space of RL models.
We improve the state-of-the-art through two agent classes designed to act on a per-flow basis, supported by an in-depth investigation of feature suitability and empirical evaluation.
